% !TEX TS-program = xelatex
% !BIB TS-program = bibtex
\documentclass[12pt,letterpaper]{article}
\usepackage{style/dsc180reportstyle} % import dsc180reportstyle.sty

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Title and Authors
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Toward Accelerated LLM Inference:\\Porting and Evaluating Diffusion-Based Speculative Decoding on TPU}

\author{Aaron Feng \\
  {\tt zhf004@ucsd.edu} \\\And
  Zhongyan Luo \\
  {\tt zhl203@ucsd.edu} \\\And
  Son Nguyen \\
  {\tt hpn005@ucsd.edu} \\\And
  Andy Huang \\
  {\tt anh031@ucsd.edu} \\\AND
  Yiming Zhao (TA) \\
  {\tt yiz279@ucsd.edu} \\\And
  Hao Zhang (Mentor) \\
  {\tt haz094@ucsd.edu} \\}

\begin{document}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Abstract and Links
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}
Large language model inference is bottlenecked by sequential autoregressive decoding. Speculative decoding alleviates this by using a fast draft model to propose tokens that are verified in parallel by the target model. DFlash is a recent speculative decoding method that replaces autoregressive drafting with a lightweight block diffusion model, generating 16 draft tokens in a single forward pass and achieving over 5$\times$ speedup on GPU. However, DFlash has only been implemented for GPU (PyTorch). In this work, we port DFlash to Google Cloud TPUs by reimplementing the algorithm in JAX within the \texttt{tpu-inference} framework. Our TPU implementation achieves an average acceptance length of $\tau=6.67$ across four math reasoning benchmarks (94\% of the original DFlash $\tau=7.07$ on GPU) and a 4.29$\times$ end-to-end speedup on a single TPU v4 device. On Math500, our TPU $\tau$ of 8.72 exceeds the original 7.84. We also integrate DFlash into the full vLLM serving pipeline on TPU, achieving 2.31$\times$ speedup. The implementation requires zero changes to vLLM and adds DFlash as a new speculative decoding method alongside the existing Eagle3 support in \texttt{tpu-inference}. We verify output quality by comparing DFlash generations against the autoregressive baseline token-by-token, confirming that 7/8 samples produce identical final answers on GSM8K, with divergences attributable to bf16 numerical precision rather than algorithmic error.
\end{abstract}

\begin{center}
Code: \url{https://github.com/aaronzhfeng/tpu-spec-decode} \\
Code: \url{https://github.com/aaronzhfeng/tpu-inference}
\end{center}

\maketoc
\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Main Contents
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

Autoregressive large language models (LLMs) generate text one token at a time: each token depends on all previously generated tokens, requiring a separate forward pass per output token. This sequential bottleneck dominates inference latency, particularly for long-form generation tasks such as chain-of-thought reasoning, where models may produce hundreds or thousands of tokens. As LLMs are deployed in latency-sensitive applications, reducing this per-token cost has become a central systems challenge.

\textbf{Speculative decoding} \citep{leviathan2023fastinferencetransformersspeculative} addresses this bottleneck by introducing a two-stage process: a lightweight \emph{draft model} quickly proposes a sequence of candidate tokens, and the full \emph{target model} verifies them in a single batched forward pass. Correctly predicted tokens are accepted for free; the first incorrect token triggers a fallback to the target model's own prediction. In the best case, many tokens are accepted per verification step, amortizing the cost of the target model's forward pass. The key metric is the \emph{acceptance length} $\tau$: the average number of tokens accepted per speculative step. Higher $\tau$ means more tokens generated per target-model call, yielding greater speedup.

Most existing speculative decoding methods, including Eagle3 \citep{li2025eagle3scalinginferenceacceleration}, Medusa \citep{cai2024medusasimplellminference}, and prompt lookup decoding, use autoregressive draft models that generate candidate tokens sequentially. While the draft model is cheaper than the target, the sequential drafting still limits throughput and introduces error accumulation, capping practical speedups at 2--3$\times$.

\textbf{DFlash} \citep{chen2026dflashblockdiffusionflash} takes a fundamentally different approach: it replaces the autoregressive drafter with a lightweight \emph{block diffusion model} that generates an entire block of 16 draft tokens in a single forward pass. The draft model is conditioned on hidden-state features extracted from the target model's intermediate layers, enabling high-quality parallel drafting without sequential dependencies between draft positions. On GPU, DFlash achieves over 5$\times$ speedup, substantially outperforming Eagle3's 2$\times$.

However, DFlash has only been implemented for GPU using PyTorch. Google Cloud TPUs offer a compelling alternative platform: their architecture, optimized for large, dense matrix operations with high memory bandwidth, is naturally suited to the parallel block-prediction pattern of diffusion-style drafting. The \texttt{tpu-inference} framework \citep{tpuinference} provides TPU support for vLLM with speculative decoding infrastructure (currently supporting Eagle3 and n-gram methods), but lacks a DFlash implementation.

\textbf{Our contribution.} We port DFlash from GPU/PyTorch to TPU/JAX, implementing the full algorithm within \texttt{tpu-inference}. We validate the port against the original paper's results on four math reasoning benchmarks (GSM8K, Math500, AIME24, AIME25), achieving 94\% of GPU draft quality ($\tau=6.67$ vs.\ 7.07) and 4.29$\times$ speedup on a single TPU v4 device. We also integrate DFlash into the vLLM serving pipeline, achieving 2.31$\times$ speedup, and verify that the implementation does not degrade output quality. Beyond replication, this work establishes a foundation for investigating the broader interaction between speculative decoding, diffusion models, and TPU hardware, a direction we argue is particularly promising given TPU's architectural affinity for the dense, parallel computation that diffusion-based methods require.


\section{Background}

\subsection{Speculative Decoding}

In standard autoregressive decoding, generating $n$ tokens requires $n$ sequential forward passes through the target model. Speculative decoding \citep{leviathan2023fastinferencetransformersspeculative} reduces this by introducing a draft-then-verify paradigm. Given the current context, a draft model proposes $k$ candidate tokens. The target model then processes all $k$ tokens in a single forward pass (similar to prefilling), producing logits at each position. The verification step compares draft tokens against the target's predictions: consecutive matches from the first position are accepted, and the first mismatch triggers rejection. If $m$ tokens are accepted ($m \leq k$), then the target model also provides the correct token at position $m+1$, yielding $m+1$ new tokens from a single target forward pass.

The expected speedup depends on the acceptance length $\tau$ (average tokens accepted per step) and the relative cost of drafting versus target verification. Higher $\tau$ means fewer target forward passes per generated token.

\subsection{DFlash: Block Diffusion for Speculative Decoding}

DFlash \citep{chen2026dflashblockdiffusionflash} replaces the autoregressive drafter with a block diffusion model. The key components are:

\begin{enumerate}
    \item \textbf{Target feature extraction.} During each target model forward pass, hidden states from a subset of intermediate layers (e.g., layers 1, 9, 17, 25, 33 for Qwen3-4B) are concatenated and projected to produce a context vector that summarizes the target model's ``reasoning state.''
    \item \textbf{Parallel block drafting.} The draft model receives (a) the context vector from the target, and (b) a noise block: the embedding of the last accepted token followed by mask tokens at 15 unknown positions. In a single forward pass with \emph{non-causal} attention over the block, the draft model predicts logits at all 16 positions simultaneously.
    \item \textbf{Shared vocabulary.} The draft model has no embedding layer or language model head of its own. It reuses the target model's \texttt{embed\_tokens} for input and the target's LM head for computing output logits, ensuring draft and target operate in the same vocabulary space.
    \item \textbf{Verification and acceptance.} The full block of 16 tokens is verified by the target model in one forward pass. Consecutive matches are accepted, and the bonus token from the target extends the sequence.
\end{enumerate}

On GPU (H200), DFlash achieves $\tau=7.07$ and 5.53$\times$ average speedup on Qwen3-4B across four math reasoning datasets, substantially outperforming Eagle3's $\tau=3.40$ and 2.02$\times$ \citep{chen2026dflashblockdiffusionflash}.

\subsection{TPU Inference and vLLM}

vLLM \citep{kwon2023efficientmemorymanagementlarge} is a high-throughput LLM serving engine that provides continuous batching, PagedAttention for efficient KV cache management, and scheduling for concurrent requests. The \texttt{tpu-inference} plugin \citep{tpuinference} adapts vLLM to run on Google Cloud TPUs, implementing model execution and attention in JAX. It supports speculative decoding via a modular \texttt{SpeculativeDecodingManager} that coordinates draft proposal, target verification, and token acceptance. Prior to our work, only Eagle3 and n-gram drafting were supported.


\section{Methods}

Porting DFlash from GPU/PyTorch to TPU/JAX required addressing several architectural mismatches between the two platforms. We describe the three main technical challenges and our solutions.

\subsection{Dual KV Cache Architecture}

The GPU DFlash implementation uses PyTorch's \texttt{DynamicCache} with simple concatenation-based KV management for both the target and draft models. On TPU, the target model uses \emph{paged attention} with Pallas kernels (\texttt{ragged\_paged\_attention}), which stores KV entries in fixed-size pages managed by block tables. The draft model's non-causal attention pattern is incompatible with paged attention.

We implemented a \textbf{dual-cache architecture}: the target model retains its paged KV cache (required for \texttt{ragged\_paged\_attention}), while the draft model uses static on-device JAX arrays with \texttt{dynamic\_update\_slice} writes and a \texttt{cache\_len} pointer for crop semantics. The draft model uses TPU's \texttt{flash\_attention} kernel with \texttt{causal=False}, matching DFlash's non-causal block diffusion design.

\subsection{Context Buffer Management}

DFlash's draft model is conditioned on projected hidden states from the target model, accumulated across iterations in a \emph{context buffer}. The GPU implementation manages this in host-side numpy arrays with power-of-2 padding for efficient TPU transfers. We replicated this pattern: after each target model forward pass, newly projected features are appended to the context buffer, padded to the next power of two, and passed to the draft model alongside a \texttt{cache\_len} and \texttt{actual\_ctx\_count} to indicate which features are new. This required careful tracking of \texttt{prev\_ctx\_len} (how much context the draft model has already consumed) to avoid feeding duplicate or missing context.

\subsection{The Sequence Length Inflation Bug}

After the initial integration into the vLLM pipeline, acceptance rates were stuck around 10\% ($\tau=2.49$, 1.30$\times$ speedup). We ran 13 systematic A/B tests (toggling flash attention, position schemes, cache modes), all inconclusive. The root cause was upstream of the proposer: the speculative decoding manager passed \texttt{attn\_metadata.seq\_lens} to the proposer, but during verification steps this value includes all draft tokens being verified (e.g., \texttt{seq\_len=116} when the true accepted count is 100). Since DFlash is the only proposer that maintains persistent state across iterations (context buffer, KV cache positions, RoPE offsets), this 10--16 token inflation silently corrupted every iteration.

The fix was four lines: read the actual accepted count from \texttt{num\_tokens\_no\_spec} and pass a corrected \texttt{attn\_metadata} to the proposer. This single change nearly doubled performance: $\tau$ jumped from 2.49 to 4.48, speedup from 1.30$\times$ to 2.31$\times$.

\subsection{Standalone Benchmark}

To provide an apples-to-apples comparison with the original DFlash results on GPU (which report standalone numbers without serving overhead) and to prove vLLM independence, we built a standalone JAX benchmark (\texttt{benchmarks/standalone\_dflash.py}). This script loads models directly via \texttt{get\_flax\_model()}, runs a prefill-draft-verify-accept loop, and tracks context buffers and KV state manually, using only existing \texttt{tpu-inference} library imports (\texttt{ModelConfig}, \texttt{LoadConfig}, model loader). No vLLM engine, scheduler, or serving pipeline is involved.


\section{Results}

We evaluate on four math reasoning datasets used in the DFlash paper: GSM8K, Math500, AIME24, and AIME25. All experiments use Qwen3-4B as the target model and z-lab/Qwen3-4B-DFlash-b16 as the draft model, with greedy decoding (temperature = 0), block size = 16, and 8 samples per dataset (7 measured, 1 warmup for JIT compilation).

\subsection{Standalone Benchmark: TPU vs.\ Original DFlash (GPU)}

Table \ref{tab:standalone} shows our standalone TPU results compared with the original DFlash numbers on GPU.

\begin{table}[htbp]
\caption{Standalone benchmark results: TPU (single v4 device, JAX) vs.\ original DFlash on GPU (H200, PyTorch). $\tau$ = average acceptance length, Speedup = wall-clock ratio over autoregressive baseline, TPS = tokens per second.}
\label{tab:standalone}
\resizebox{\linewidth}{!}{\input{table/standalone_results}}
\end{table}

Our TPU implementation achieves $\tau=6.67$ on average, which is 94\% of the original DFlash $\tau=7.07$ on GPU. On Math500, our TPU $\tau$ of 8.72 \textbf{exceeds} the original 7.84. The average end-to-end speedup is 4.29$\times$ compared to the original 5.53$\times$ on GPU. The remaining speedup gap is primarily due to hardware differences (TPU v4 vs.\ H200 GPU) rather than algorithm quality, as the $\tau$ ratio is much closer than the speedup ratio.

\subsection{vLLM Pipeline Integration}

We also integrated DFlash into the full vLLM serving pipeline on TPU (4 TPU v4 devices). Table \ref{tab:cross} shows the cross-comparison.

\begin{table}[htbp]
\caption{Cross-comparison: standalone TPU, vLLM pipeline TPU, and original DFlash (GPU). The vLLM pipeline shows lower speedup due to scheduling and batch management overhead, not algorithm quality.}
\label{tab:cross}
\resizebox{\linewidth}{!}{\input{table/cross_comparison}}
\end{table}

The vLLM pipeline achieves $\tau=4.48$ and 2.31$\times$ speedup (212 TPS vs.\ 92 TPS baseline). The lower numbers compared to the standalone benchmark are expected: vLLM's scheduler, batch manager, and rejection sampling loop add per-step overhead that compounds across speculative decoding iterations. This matches the GPU side, where the paper's standalone results are also significantly better than their serving numbers. Furthermore, vLLM's TPU v4 support is listed as experimental; we plan to rerun on v5 TPU (where vLLM is fully supported) once our requested instance becomes available.

\subsection{Comparison with Eagle3}

The only other speculative decoding method available on TPU through \texttt{tpu-inference} is Eagle3. Table \ref{tab:eagle3} compares DFlash and Eagle3 on the same vLLM pipeline.

\begin{table}[htbp]
\caption{DFlash vs.\ Eagle3 on the vLLM TPU pipeline. Different target models (Qwen3-4B vs.\ Llama-3.1-8B), so not a direct head-to-head, but shows the advantage of block diffusion (15 tokens/step) over autoregressive drafting (3 tokens/step).}
\label{tab:eagle3}
\resizebox{0.85\linewidth}{!}{\input{table/eagle3_comparison}}
\end{table}

DFlash's $\tau$ is 2.06$\times$ that of Eagle3 (4.48 vs.\ 2.18) and its speedup is 1.51$\times$ that of Eagle3 (2.31$\times$ vs.\ 1.53$\times$). These ratios closely match the original DFlash proportional advantage on GPU: DFlash's $\tau$ is 1.91$\times$ Eagle3's (6.49 vs.\ 3.40). This suggests DFlash's fundamental advantage over autoregressive drafting transfers well across hardware platforms.

\subsection{Output Quality Verification}

Speculative decoding with greedy sampling is mathematically guaranteed to produce the same output as autoregressive decoding under exact arithmetic. In practice, bf16 numerical precision can cause minor divergences. We verified output quality by comparing DFlash generations against the autoregressive baseline token-by-token on GSM8K (8 samples, 1024 max tokens).

\begin{table}[htbp]
\caption{Output quality check on GSM8K. 4/8 samples produce bit-exact identical output; 7/8 arrive at the same final $\backslash$\texttt{boxed\{\}} math answer. Divergences occur at random positions where top-2 logits are close, consistent with bf16 precision effects.}
\label{tab:quality}
\resizebox{\linewidth}{!}{\input{table/quality_check}}
\end{table}

As shown in Table \ref{tab:quality}, 4 out of 8 samples produce bit-exact identical output. The remaining 4 samples diverge at a single token position (positions 8, 13, 68, and 245), after which subsequent tokens cascade differently due to autoregressive dependencies. Despite these divergences, 7 out of 8 samples arrive at the same final boxed answer. The one answer difference (452 vs.\ 470) stems from an early divergence at token 68 where the model chooses a different number, leading to a different arithmetic path. The divergence points show coherent alternative text (e.g., \texttt{**Indras**} vs.\ \texttt{Indras}, \texttt{Step 1:} vs.\ \texttt{Initial Setup:}), confirming these are decision-boundary effects, not corruption. DFlash does not degrade model intelligence.


\section{Discussion}

\subsection{Why Is the Standalone Faster Than vLLM?}

The standalone benchmark achieves 4.29$\times$ speedup while the vLLM pipeline achieves 2.31$\times$, despite using the same model and algorithm. This is because vLLM is a \emph{serving} framework designed for high-throughput concurrent request handling, not single-request latency. Its scheduler, batch manager, PagedAttention bookkeeping, and rejection sampling loop add per-step overhead. Speculative decoding amplifies this overhead because it performs more round trips (draft + verify) per generated token than standard decoding. The original DFlash results show the same pattern: standalone numbers are substantially better than their SGLang serving numbers.

Notably, our vLLM benchmark runs requests sequentially (\texttt{max\_num\_seqs=1}), which represents the worst case for vLLM: all scheduling overhead with no batching benefit. The original DFlash serving benchmarks use concurrent requests (concurrency 1--32) with a ThreadPoolExecutor. A fairer serving comparison on TPU would require running vLLM in online serving mode with concurrent clients, which we leave to future work.

\subsection{TPU vs.\ GPU: Where Does the Gap Come From?}

Our $\tau$ (6.67) is 94\% of the original DFlash $\tau$ on GPU (7.07), but our speedup (4.29$\times$) is 78\% of the original (5.53$\times$). The $\tau$ gap is small and may be attributable to minor differences in model weight precision or attention kernel numerics. The larger speedup gap likely comes from hardware characteristics: the H200 GPU has higher memory bandwidth and may have faster kernel dispatch for the specific computation patterns in speculative decoding (repeated small matrix operations with varying shapes).

\subsection{vLLM Independence}

A key design goal was ensuring the DFlash implementation has \textbf{zero dependency on vLLM changes}. The standalone benchmark imports only \texttt{ModelConfig} and \texttt{LoadConfig} from vLLM, which are existing \texttt{tpu-inference} dependencies used by every model. No new vLLM code is required. The vLLM serving integration requires only a $\sim$10-line config change in a separate repository, which can be upstreamed independently. This means a pull request to \texttt{tpu-inference} can proceed without any coordination with the vLLM project.


\section{Future Work}

With the DFlash TPU replication validated, we see two categories of next steps: near-term engineering work and longer-term research directions at the intersection of speculative decoding, diffusion models, and TPU hardware.

\subsection{Near-Term Engineering}

\begin{enumerate}
    \item \textbf{Pull request to \texttt{tpu-inference}.} Prepare and submit the DFlash implementation (model, proposer, standalone benchmark, seq\_len fix) as a contribution to the upstream repository.
    \item \textbf{TPU v5 benchmarks.} Our current results are on TPU v4, where vLLM support is listed as experimental. We have requested a v5 instance and plan to rerun all benchmarks, as vLLM lists v5 as fully supported.
    \item \textbf{Concurrent serving benchmarks.} Run the vLLM pipeline with multiple concurrent clients at various concurrency levels (1, 4, 8, 16, 32) to match the original DFlash serving evaluation methodology and measure throughput scaling.
    \item \textbf{Multi-device standalone.} Add \texttt{shard\_map} wrapping for the \texttt{flash\_attention} Pallas kernel to enable multi-device standalone runs.
\end{enumerate}

\subsection{Speculative Decoding and Diffusion Models on TPU}

Our DFlash port raises a broader research question: \textit{how do speculative decoding methods interact with diffusion-based generation on TPU?} To our knowledge, no prior work has benchmarked diffusion-based speculative decoding on TPU, making our DFlash port the first data point in this space.

DFlash uses a diffusion model as a \emph{drafter} for an autoregressive target, but diffusion language models (dLLMs) are increasingly used as the \emph{target} model itself. Recent work such as FailFast \citep{pan2026failfastwinbig} explores speculative decoding where both the drafter and verifier operate in the diffusion paradigm, with adaptive speculation lengths based on drafter confidence. This is complementary to our work: while DFlash accelerates autoregressive targets with diffusion drafting, FailFast accelerates diffusion targets with speculative verification.

One hypothesis worth investigating is whether TPU hardware is particularly well-suited to diffusion-based speculative decoding. Diffusion models rely on dense, parallel matrix operations over blocks of tokens rather than sequential token-by-token generation. TPU systolic arrays are designed for such data-parallel workloads. Recent work on compute-in-memory TPU architectures has shown that compute-bound workloads (such as image Diffusion Transformers) benefit more from TPU scaling than memory-bound workloads like autoregressive decoding \citep{wang2025acceleratinglargelanguagemodel}. Whether this advantage extends to discrete diffusion language models remains an open question that has not been empirically tested.

We plan to investigate these directions by: (1) benchmarking diffusion language models (e.g., Fast-dLLM) as both drafters and targets on TPU, (2) evaluating whether the FailFast adaptive speculation strategy transfers to TPU hardware, and (3) comparing TPU vs.\ GPU speedups for diffusion-based vs.\ autoregressive-based speculative decoding to test whether the hypothesized TPU advantage holds in practice.


\section{Conclusion}

We have successfully ported DFlash speculative decoding from GPU/PyTorch to TPU/JAX, achieving 94\% of the original paper's draft quality ($\tau=6.67$ vs.\ 7.07) and 4.29$\times$ speedup on a single TPU v4 device. On Math500, our TPU implementation actually exceeds the original DFlash on GPU ($\tau=8.72$ vs.\ 7.84). The vLLM pipeline integration achieves 2.31$\times$ speedup with zero new vLLM dependencies. Output quality verification confirms DFlash does not degrade model intelligence: 7/8 samples produce the same final answer as the baseline, with divergences attributable to bf16 precision. DFlash's advantage over autoregressive drafting (Eagle3) transfers proportionally from GPU to TPU, validating the algorithm's hardware-agnostic design. The implementation is ready for contribution to the \texttt{tpu-inference} repository.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Reference / Bibliography
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\makereference

\bibliography{reference}
\bibliographystyle{style/dsc180bibstyle}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Appendix
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\makeappendix

\subsection{Files Modified in \texttt{tpu-inference}}

\begin{table}[htbp]
\caption{Files added or modified for the DFlash TPU port.}
\centering
\begin{tabular}{l|l}
\toprule
File & Change \\
\midrule
\texttt{models/jax/dflash.py} & DFlash model (new) \\
\texttt{spec\_decode/jax/dflash.py} & DFlash proposer (new) \\
\texttt{runner/speculative\_decoding\_manager.py} & seq\_len fix + DFlash integration \\
\texttt{benchmarks/standalone\_dflash.py} & Standalone benchmark (new) \\
\texttt{tests/standalone\_benchmark.sh} & Docker wrapper (new) \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Reproduction Commands}

\begin{verbatim}
# Standalone benchmark (single dataset)
DATASET=math500 bash tests/standalone_benchmark.sh \
  --max-samples 8 --max-new-tokens 256

# All four datasets
for ds in gsm8k math500 aime24 aime25; do
  DATASET=$ds bash tests/standalone_benchmark.sh \
    --max-samples 8 --max-new-tokens 256
done

# vLLM pipeline benchmark
bash tests/benchmark.sh math
\end{verbatim}


\end{document}
